Texture Mapping 3D Planar Models of Indoor Environments with Noisy Camera Poses

### 2012-12-23 spie/assets/_region_.tex
starting spie stuff

\documentclass[10pt,twocolumn,letterpaper]{article}

@@

%%%%%%%%% TITLE
\title{Texture Mapping 3D Models of Indoor Environments with Noisy
  Camera Poses}

\author{First Author\\
  Institution1\\
  Institution1 address\\
  {\tt\small firstauthor@i1.org}
  % For a paper whose authors are all at the same institution, omit
  % the following lines up until the closing ``}''.  Additional
  % authors and addresses can be added with ``\and'', just like the
  % second author.  To save space, use either the email address or
  % home page, not both
  \and
  Second Author\\
  Institution2\\
  First line of institution2 address\\
  {\small\url{http://www.author.org/~second}} }

\maketitle
% \thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
  Automated 3D modeling of building interiors is useful in
  applications such as virtual reality and environment
  mapping. Applying textures to these models is an important step in
  generating photorealistic visualizations of data collected by
  modeling systems. Camera pose recovery in such systems often suffers
  from inaccuracies, resulting in visible discontinuties when
  successive images are projected adjacently onto a plane for
  texturing. We propose two approaches to reduce discontinuities in
  texture mapping 3D models made of planar surfaces. The first one is
  tile based and can be used for images and planes at arbitrary angles
  relative to each other. The second one results in a more seamless
  texture, but is only applicable where camera axes for images are
  closely aligned with plane normals of the surfaces to be
  textured. The effectiveness of our approaches are demonstrated on
  two indoor datasets.
\end{abstract}

@@

>>>>

\message{ !name(oldpaper.tex)}\documentclass[10pt,twocolumn,letterpaper]{article}

@@

\message{ !name(oldpaper.tex) !offset(-3) }

%%%%%%%%% TITLE
\title{Texture Mapping 3D Planar Models of Indoor Environments with Noisy
  Camera Poses}

\author{Peter Cheng \hspace*{2em} Michael Anderson \hspace*{2em} Stewart He \hspace*{2em} Avideh Zakhor\\
  UC Berkeley\\
}
\maketitle
% \thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
  Automated 3D modeling of building interiors is useful in
  applications such as virtual reality and environment
  mapping. Applying textures to these models is an important step in
  generating photorealistic visualizations of data collected by
  modeling systems. Camera pose recovery in such systems often suffers
  from inaccuracies, resulting in visible discontinuities when
  successive images are projected adjacently onto a plane for
  texturing. We propose two approaches to reduce discontinuities in
  texture mapping 3D models made of planar surfaces. The first one is
  tile based and can be used for images and planes at arbitrary angles
  relative to each other. The second one results in a more seamless
  texture, but is only applicable where camera axes for images are
  closely aligned with plane normals of the surfaces to be
  textured. The effectiveness of our approaches are demonstrated on
  two indoor datasets.
\end{abstract}

@@

\message{ !name(oldpaper.tex) !offset(-739) }
